---
title: "R Notebook"
output: html_notebook
---
mlizhang@gmail.com
UCSFairrR01R21!

list of common TAAs:
CEA
CA 19-9
CA 72-4
Claudin 18.2 *
HER2 *
NY-ESO-1
MAGE class (as for HCC, not entirely specific but may be expressed)

*approved therapy targeting it

This paper has more listed and also may be of interest as they identified T cell responses: https://jitc.bmj.com/content/10/12/e005200

list of associated infections:
H pylori (bacterial)
EBV
possibly related but not clearly causal - HBV, HPV, CMV
# Read the prediction results
```{r}
library(tidyverse)
library(NAIR)
```
```{r}
tissue <- read_csv("./Apexigen_data/PBMC_tumor_metadata_TCR_match.csv") %>% mutate(timepoint_sample = paste(sample, timepoint,sep = "_"), barcode = paste(TRB_barcode,sample, sep = "_")) 
```
```{r}
apexigen_pred <- read_csv("./Apexigen_tumor_paired_train_all_pred_res_IEDB_McPAS_VDJdb_081_acc_042226.csv")
```


```{r}
Apexigen_meta <- read_csv('./Apexigen_data/Apexigen_obs_metadata_for_integration_real_case.csv')
```

```{r}
all_3_datasets_peptide_type <-  readr::read_csv("all_3_datasets_peptide_type.csv") %>% filter(!is.na(Epitope_type))
```
```{r}
all_3_datasets_peptide_type_viral <- all_3_datasets_peptide_type %>% filter(str_detect(str_to_lower(Epitope_type),"hepatitis b|hepatitis c|barr"))
```

```{r}
all_3_datasets_peptide_type_tumor <- all_3_datasets_peptide_type %>% filter(str_detect(str_to_lower(Epitope_type),"mela|cancer|tyrosinase|tumor|syt-ssx2|mage|ny-eso|tyrosine|cea|her2|Claudin"))
```


```{r}
all_3_datasets_peptide_type %>% filter(str_detect(Epitope_type,"MAGE"))

all_3_datasets_peptide_type %>% filter(peptide_cat == "Tumor")
```

```{r}
apexigen_pred$barcode <- rep(Apexigen_meta$...1, 1337)
apexigen_pred <- apexigen_pred %>% left_join(all_3_datasets_peptide_type, join_by("Epitope"))
```
```{r}
apexigen_pred %>% filter(str_detect(Epitope_type,"NY-ESO")) %>% filter(predicted_binding_probability > 0.5)
```
```{r}
apexigen_pred %>% filter(str_detect(Epitope_type,"MAGE")) %>% filter(predicted_binding_probability > 0.5)
```

```{r}
apexigen_pred <- apexigen_pred %>% filter(!is.na(Epitope_type))
```
```{r}
res_tumor <- apexigen_pred %>% filter(Epitope %in%all_3_datasets_peptide_type_tumor$Epitope)
res_tumor_high_prob <- res_tumor %>% group_by(barcode) %>% arrange(desc(predicted_binding_probability)) %>% filter(row_number() == 1) %>% filter(predicted_binding_probability > 0.6) %>% filter(str_length(Epitope_type) > 8)
res_tumor_high_prob$peptide_cat <- "Tumor"
```
```{r}
res_viral <- apexigen_pred %>% filter(Epitope %in%all_3_datasets_peptide_type_viral$Epitope)
res_viral_high_prob <- res_viral %>% group_by(barcode) %>% arrange(desc(predicted_binding_probability)) %>% filter(row_number() == 1) %>% filter(predicted_binding_probability > 0.8) %>% filter(str_length(Epitope_type) > 8)
res_viral_high_prob$peptide_cat <- "Viral"
```
```{r}
length(unique(res_viral_high_prob$barcode) )
```
```{r}
tumor_viral <- rbind(res_tumor_high_prob,res_viral_high_prob) %>% group_by(barcode) %>% arrange(desc(predicted_binding_probability)) %>% filter(row_number() == 1)
```
```{r}
table(tumor_viral$peptide_cat)
```
```{r}
others_type <- apexigen_pred %>% group_by(barcode) %>% arrange(desc(predicted_binding_probability)) %>% filter(row_number() == 1) %>% filter(!(barcode %in% tumor_viral$barcode))
others_type$peptide_cat <- "others"
```

```{r}
dat_network <- rbind(tumor_viral,others_type)
```
```{r}
dat_network <- dat_network %>% filter(!str_detect(patient, "HD"))
```
```{r}
table(dat_network$patient)
```

```{r}
res_tumor_selected_virus <- buildNet(dat_network,
                                              seq_col = "TRB_cdr3", #
                              color_nodes_by = c("peptide_cat"),
                              min_seq_length = 1,
                              dist_cutoff = 0,
                              output_dir = "./network_res",
                              drop_isolated_nodes = TRUE,
                              dist_type = "hamming",
                              stats_to_include = "all",
                              node_stats = TRUE,
                              cluster_stats = TRUE,
                              plots = TRUE
                )

res_tumor_selected_virus <- readRDS("./network_res/MyRepSeqNetwork.rds")
```
```{r}
table(dat_network$peptide_cat)
```

```{r}
write_csv(dat_network,"dat_network.csv")
```


```{r}
table(tissue$tissue)
```

```{r}

tissue_barcode <- tissue %>% filter(barcode %in% res_tumor_selected_virus$node_data$barcode)
res_tumor_selected_virus$node_data <- res_tumor_selected_virus$node_data %>% mutate(timepoint_sample = paste(sample, timepoint,sep = "_")) %>% left_join(tissue_barcode, join_by("barcode"))
```

```{r}
write.csv(res_tumor_selected_virus$node_data,"network_results_Apexigen.csv")
```


```{r}



length(unique(res_tumor_selected_virus$node_data$barcode))
table(tissue$tissue)
table(res_tumor_selected_virus$node_data$timepoint)
table(res_tumor_selected_virus$node_data$timepoint)
```

```{r}
addPlots(res_tumor_selected_virus,color_nodes_by = "cluster_id")
```

```{r}
Apexigen_exact_match_IEDB_McPAS_VDJdb_epitope <- read_csv("./Apexigen_match_full_IEDB_McPAS_VDJdb_all_data.csv") %>% select(CDR3,Epitope) %>% unique() %>% mutate(CDR_epitope = paste(CDR3,Epitope,sep = "_"))
Apexigen_exact_match_IEDB_McPAS_VDJdb_epitope
```
```{r}
res_tumor_selected_virus$node_data <- res_tumor_selected_virus$node_data %>% mutate(exact_match = ifelse(TCR_Epitope_pair %in% Apexigen_exact_match_IEDB_McPAS_VDJdb_epitope$CDR_epitope, "Match",NA))
```

```{r}
library(igraph)
```
```{r}
res_tumor_selected_virus$node_data <- res_tumor_selected_virus$node_data %>% mutate(color_code = ifelse(peptide_cat == "Tumor","red",ifelse(peptide_cat == "Viral","blue","lightgrey")))
g <- res_tumor_selected_virus$igraph
V(g)$color <- res_tumor_selected_virus$node_data$color_code
# V(g)$label <- NA
plot(
  g,
  layout = res_tumor_selected_virus$plots$graph_layout,          # Use our coordinates
  vertex.size = 1,
  vertex.color = V(g)$color,
  vertex.label = NA,
  # edge.color = "gray40",
)



```

```{r}
pdf("tumor_viral_others.pdf", width = 16, height = 10)
# shared$plots$graph_layout

g <- res_tumor_selected_virus$igraph
col_code <- res_tumor_selected_virus$node_data$peptide_cat
# col_pal <- colorRampPalette(c( "red", "#007FFF", "grey"))
col_code <- as.character(col_code)
# col_code <- factor(col_code)
v_color_factor <- as.factor(col_code)

pal <- c("lightgrey","red","green")
names(pal) <- levels(v_color_factor)
ver_color <- pal[v_color_factor]
unique(ver_color)
# ver_color[is.na(ver_color)] <- "white"
par(mar = c(1, 1, 1, 1))

plot(g, layout = as.matrix(res_tumor_selected_virus$plots$graph_layout), vertex.label = NA, vertex.size = 3, vertex.color = ver_color, main = "Prediction")
dev.off()
```
```{r}
table(col_code, useNA="always")
dim(as.matrix(res_tumor_selected_virus$plots$graph_layout))
```
```{r}
table(col_code, useNA="always")
```

```{r}
res_tumor_selected_virus$node_data$peptide_cat_col <- ifelse(res_tumor_selected_virus$node_data$peptide_cat != "others",res_tumor_selected_virus$node_data$peptide_cat,NA)
```

```{r}
addPlots(res_tumor_selected_virus,color_nodes_by = "peptide_cat_col")
```
```{r}
addPlots(res_tumor_selected_virus,color_nodes_by = "exact_match")
```
```{r}
addPlots(res_tumor_selected_virus,color_nodes_by = "patient")
```

```{r}
res_tumor_selected_virus$node_data %>% group_by(cluster_id) %>% summarise(n_size = n())
```
```{r}
res_tumor_selected_virus$node_data %>% filter(peptide_cat_col == "Tumor") %>% group_by(cluster_id) %>% summarise(n_size = n())
```
```{r}
res_tumor_selected_virus$node_data %>% filter(cluster_id == 4) 
```

```{r}
addPlots(res_tumor_selected_virus, color_nodes_by = "cluster_id")
```


```{r}
res_tumor_selected_virus$node_data %>% filter(!is.na(exact_match))
```

```{r}

res_tumor_selected_virus_new <- buildNet(res_tumor_selected_virus$node_data,
                                              seq_col = "TRB_cdr3", #
                              color_nodes_by = c("peptide_cat_col","exact_match","patient"),
                              min_seq_length = 1,
                              dist_cutoff = 0,
                              output_dir = "./network_res",
                              drop_isolated_nodes = TRUE,
                              dist_type = "hamming",
                              stats_to_include = "all",
                              node_stats = TRUE,
                              cluster_stats = TRUE,
                              plots = TRUE,
                              # color_scheme = "plasma-1"
                )
```
```{r}
# hepatitis b|hepatitis c|barr
# "mela|cancer|tyrosinase|tumor|syt-ssx2|mage|ny-eso|tyrosine|cea|her2|Claudin"
dat_network <- dat_network %>%
  mutate(
    peptide_class = case_when(
      str_detect(str_to_lower(Epitope_type), "hepatitis b") ~ "Hepatitis B",
      str_detect(str_to_lower(Epitope_type), "hepatitis c") ~ "Hepatitis C",
      str_detect(str_to_lower(Epitope_type), "barr") ~ "Epstein Barr virus",
      str_detect(str_to_lower(Epitope_type), "mela") ~ "Melanoma",
      str_detect(str_to_lower(Epitope_type), "testis antigen 1_Homo sapiens") ~ "Cancer/testis antigen",
      str_detect(str_to_lower(Epitope_type), "tumor antigen p53") ~ "Cellular tumor antigen p53",
      str_detect(str_to_lower(Epitope_type), "mage") ~ Epitope_type,
      str_detect(str_to_lower(Epitope_type), "ny-eso") ~ "NY-ESO",
      str_detect(str_to_lower(Epitope_type), "tyrosi") ~ "Tyrosine",
      str_detect(str_to_lower(Epitope_type), "her2") ~ "HER2",
      str_detect(str_to_lower(Epitope_type), "cea") ~ "CEA",
      TRUE ~ NA_character_
    )
  )
table(dat_network$peptide_cat,dat_network$Epitope_type)
table(dat_network$Epitope_type)
table(dat_network$peptide_class)
```
```{r}
# cell_map = data_frame('CD4T_naive2':'CD4T_naive',
#  'CD4T_naive1':'CD4T_naive',
#  'CD8_GrH':'CD8T_GrH',
#  'CD4T_naive3':'CD4T_naive',
#  'Treg':'Treg',
#  'CD8T_prolif':'CD8T_prolif',
#  'CD8T_GrK':'CD8T_GrK',
#  'Treg1':'Treg',
#  'CD8T_GrB':'CD8T_GrB',
#  'CD4_Tnaive1':'CD4T_naive',
#  'CD8T_GrH':'CD8T_GrH',
#  'CD4_Tfh-like':'CD4_Tfh-like',
#  'Treg2':'Treg',
#  'gd_Tcell': 'gd_Tcell',
#  'MAIT':'MAIT')
res_tumor_selected_virus$node_data <- res_tumor_selected_virus$node_data %>%
  mutate(
    final_cell_type = case_when(
      str_detect((cell_type_scvi), "CD4T_naive2") ~ "CD4T_naive",
      str_detect((cell_type_scvi), "CD4T_naive1") ~ "CD4T_naive",
      str_detect((cell_type_scvi), "CD8_GrH") ~ "CD8T_GrH",
      str_detect((cell_type_scvi), "CD4T_naive3") ~ "CD4T_naive",
      str_detect((cell_type_scvi), "Treg") ~ "Treg",
      str_detect((cell_type_scvi), "CD8T_prolif") ~ "CD8T_prolif",
      str_detect((cell_type_scvi), "Treg1") ~ "Treg",
      str_detect((cell_type_scvi), "CD8T_GrK") ~ "CD8T_GrK",
      str_detect((cell_type_scvi), "CD4_Tnaive1") ~ "CD4T_naive",
      str_detect((cell_type_scvi), "CD8T_GrH") ~ "CD8T_GrH",
      str_detect((cell_type_scvi), "CD4_Tfh-like") ~ "CD4_Tfh-like",
      str_detect((cell_type_scvi), "Treg2") ~ "Treg",
      str_detect((cell_type_scvi), "gd_Tcell") ~ "gd_Tcell",
      str_detect((cell_type_scvi), "MAIT") ~ "MAIT",
      str_detect((cell_type_scvi), "CD8T_GrB") ~ "CD8T_GrB",
      TRUE ~ NA_character_
    )
  )

table(res_tumor_selected_virus$node_data$final_cell_type)
```
```{r}
addPlots(res_tumor_selected_virus,color_nodes_by = "final_cell_type")
```
```{r}
res_tumor_selected_virus$node_data <- res_tumor_selected_virus$node_data %>% group_by(cluster_id) %>% mutate(status_check = paste(sort(unique(timepoint)), collapse = "_")) %>% mutate(status_res = case_when(
  status_check == "pre_CD40" ~ "Pre-existing",
  status_check == "post_CD40_pre_CD40" ~ "Persistent",
  status_check == "post_CD40" ~ "Induced",
  status_check == "follow_up_post_CD40_post_CD40" ~ "Induced",
  status_check == "follow_up" ~ "Induced",
  status_check == "follow_up_post_CD40_pre_CD40" ~ "Persistent",
  status_check == "pre_CD40_surgery" ~ "Persistent",
  status_check == "post_CD40_surgery" ~ "Persistent",
  status_check == "follow_up_post_CD40_pre_CD40" ~ "Persistent",
  status_check == "follow_up_post_CD40_pre_CD40_surgery" ~ "Persistent",
  status_check == "follow_up_post_CD40_surgery" ~ "Induced",
  status_check == "follow_up_pre_CD40_surgery" ~ "Persistent",
  status_check == "follow_up_pre_CD40" ~ "Persistent",
  status_check == "follow_up_surgery" ~ "Induced",
  status_check == "surgery" ~ "Induced",
  status_check == "post_CD40_pre_CD40_surgery" ~ "Persistent",
  status_check == "follow_up_post_CD40" ~ "Induced",
))

table(res_tumor_selected_virus$node_data$status_res, useNA = "always")
table(res_tumor_selected_virus$node_data$status_check, useNA = "always")
```
```{r}
addPlots(res_tumor_selected_virus,color_nodes_by = "status_res")
```
```{r}
res_tumor_selected_virus$node_data %>% group_by(cluster_id) %>% mutate(cluster_size = n())
```
```{r}
res_tumor_selected_virus$node_data <- res_tumor_selected_virus$node_data %>% mutate(tissue = ifelse((sample == "05_pre") & (timepoint == "pre_CD40"),"PBMC","Tumor"))
```
```{r}
addPlots(res_tumor_selected_virus,color_nodes_by = c("tissue","status_res","timepoint","final_cell_type"))
```
```{r}


res_tumor_selected_virus$node_data <- res_tumor_selected_virus$node_data %>% mutate(timepoint_bi = ifelse(str_detect(timepoint,"pre"),"Pre","Post")) 
res_tumor_selected_virus$node_data$timepoint_bi <- factor(res_tumor_selected_virus$node_data$timepoint_bi, levels = c("Pre","Post")) 
res_tumor_selected_virus$node_data$status_res <- factor(res_tumor_selected_virus$node_data$status_res, levels = c("Pre-existing","Induced","Persistent")) 
pdf("network_plot_all.pdf")
addPlots(res_tumor_selected_virus,color_nodes_by = c("tissue","status_res","timepoint_bi","final_cell_type"))
dev.off()

saveRDS(res_tumor_selected_virus,"res_tumor_selected_virus_042826.RDS")
```

```{r}
test <- res_tumor_selected_virus$node_data %>% mutate(tissue = ifelse((sample == "05_pre") & (timepoint == "pre_CD40"),"PBMC","Tumor"))
table(test$tissue)
```
```{r}
table(tissue_barcode$timepoint_sample,tissue_barcode$tissue)
```
```{r}
res_tumor_selected_virus$node_data %>% filter((sample == "05_pre") & (timepoint == "pre_CD40"))
```

```{r}
sta_res <- as.data.frame(table(dat_network$peptide_class))
sta_res
```


```{r}
res <- apexigen_pred %>% group_by(barcode) %>% arrange(desc(predicted_binding_probability)) %>% filter(row_number() == 1)
```
```{r}
res <- res %>% mutate(predict_08 = (predicted_binding_probability >0.8))
```
```{r}
res %>% filter(peptide_cat == "Tumor")
```

```{r}
table(res$predict_08)
table(res$Epitope_type,res$peptide_cat)
```
```{r}
Apexigen_tumor_paired_train_all_peptide_no_NA_yes_peptide_type_tumor_unique_n_HD_high_conf <- read_csv("Apexigen_tumor_paired_train_all_peptide_no_NA_yes_peptide_type_tumor_unique_n_HD_high_conf_for_network_plot.csv")
```
```{r}
Apexigen_tumor_paired_train_all_peptide_no_NA_yes_peptide_type_tumor_unique_n_HD_high_conf <- Apexigen_tumor_paired_train_all_peptide_no_NA_yes_peptide_type_tumor_unique_n_HD_high_conf %>% mutate(predicted_binding_probability)
```

```{r}
library(NAIR)
```

```{r}
res <- buildNet(Apexigen_tumor_paired_train_all_peptide_no_NA_yes_peptide_type_tumor_unique_n_HD_high_conf,
                                              seq_col = "TRB_cdr3", #
                              color_nodes_by = c("peptide_cat","category"),
                              min_seq_length = 1,
                              dist_cutoff = 0,
                              output_dir = "./network_res",
                              drop_isolated_nodes = TRUE,
                              dist_type = "hamming",
                              stats_to_include = "all",
                              node_stats = TRUE,
                              cluster_stats = TRUE,
                              plots = TRUE
                )
```
```{r}
Apexigen_tumor_paired_train_all_peptide_no_NA_yes_peptide_type_tumor_unique_n_HD_high_conf %>% filter(str_detect(Epitope_type,"Bar"))
```
```{r}
res_tumor_selected_virus$node_data$cell
```
```{r}
my_manual_color <- c('CD4T_naive'= '#1f77b4',
 'CD4_Tfh-like'= '#ff7f0e',
 'CD8T_GrB'= '#2ca02c',
 'CD8T_GrH'= '#d62728',
 'CD8T_GrK'= '#9467bd',
 'CD8T_prolif'= '#8c564b',
 'MAIT'= '#e377c2',
 'Treg'= '#7f7f7f',
 'gd_Tcell'= '#bcbd22')
```


```{r}
res_tumor_selected_virus$node_data <- res_tumor_selected_virus$node_data %>%
  mutate(
    final_cell_type = case_when(
      str_detect((cell_type_scvi), "CD4T_naive2") ~ "CD4T_naive",
      str_detect((cell_type_scvi), "CD4T_naive1") ~ "CD4T_naive",
      str_detect((cell_type_scvi), "CD8_GrH") ~ "CD8T_GrH",
      str_detect((cell_type_scvi), "CD4T_naive3") ~ "CD4T_naive",
      str_detect((cell_type_scvi), "Treg") ~ "Treg",
      str_detect((cell_type_scvi), "CD8T_prolif") ~ "CD8T_prolif",
      str_detect((cell_type_scvi), "Treg1") ~ "Treg",
      str_detect((cell_type_scvi), "CD8T_GrK") ~ "CD8T_GrK",
      str_detect((cell_type_scvi), "CD4_Tnaive1") ~ "CD4T_naive",
      str_detect((cell_type_scvi), "CD8T_GrH") ~ "CD8T_GrH",
      str_detect((cell_type_scvi), "CD4_Tfh-like") ~ "CD4_Tfh-like",
      str_detect((cell_type_scvi), "Treg2") ~ "Treg",
      str_detect((cell_type_scvi), "gd_Tcell") ~ "gd_Tcell",
      str_detect((cell_type_scvi), "MAIT") ~ "MAIT",
      str_detect((cell_type_scvi), "CD8T_GrB") ~ "CD8T_GrB",
      TRUE ~ NA_character_
    )
  )

```
```{r}
res_tumor_selected_virus$node_data <- res_tumor_selected_virus$node_data %>%
  mutate(
    final_cell_type_color = case_when(
       str_detect(final_cell_type, 'CD4T_naive')~ '#1f77b4',
       str_detect(final_cell_type,  'CD4_Tfh-like')~ '#ff7f0e',
       str_detect(final_cell_type,  'CD8T_GrB')~ '#2ca02c',
       str_detect(final_cell_type,  'CD8T_GrH')~ '#d62728',
       str_detect(final_cell_type,  'CD8T_GrK')~ '#9467bd',
       str_detect(final_cell_type,  'CD8T_prolif')~ '#8c564b',
       str_detect(final_cell_type,  'MAIT')~ '#e377c2',
       str_detect(final_cell_type,  'Treg')~ '#7f7f7f',
       str_detect(final_cell_type,  'gd_Tcell')~ '#bcbd22',
      TRUE ~ NA_character_
    )
  )
```

```{r}
library(igraph)
library(ggraph)
network_celltype_graph <- res_tumor_selected_virus$igraph
network_node_dat <- res_tumor_selected_virus$node_data
network_node_dat$ix <- c(1:nrow(res_tumor_selected_virus$node_data))
network_graph_edge_color <- layer_data(res_tumor_selected_virus$plots$exact_match, 1)
network_graph_node_color <- layer_data(res_tumor_selected_virus$plots$exact_match, 2)

cl_order <- network_node_dat %>% select(final_cell_type_color,final_cell_type) %>% unique() %>% arrange(final_cell_type)
x_limits <- range(network_graph_node_color$x)
y_limits <- range(network_graph_node_color$y)


jpeg("cell_type_plot_correct_color.jpeg",width = 7, height = 7, units = "in", res = 300)
ggraph(network_celltype_graph, layout= res_tumor_selected_virus$plots$graph_layout ) + geom_edge_link(edge_width = 0.1, color = "grey") + geom_node_point(size = 0.5, aes(color = res_tumor_selected_virus$node_data$final_cell_type_color))  +
    scale_color_identity(guide = "legend", name = paste("Celltype"),
      # 1. Define the physical order of colors you want in the legend
      breaks = cl_order$final_cell_type_color, 
      
      # 2. Match the labels to the exact order of the breaks above
      labels = cl_order$final_cell_type) + coord_cartesian(xlim = x_limits, ylim = y_limits)+ guides(color = guide_legend(override.aes = list(size = 4))) + theme_void()
 dev.off()
# ggsave("cell_type_plot_correct_color.pdf", cell_type_plot_correct_color,width = 7, height = 7, units = "in")

```
```{r}
res_tumor_selected_virus$node_data %>% filter(peptide_cat == "Tumor") %>% group_by(Epitope) %>% mutate(n_epitope = n()) %>% filter(cluster_id == 4)
```
```{r}
res_tumor_selected_virus$node_data %>% filter(peptide_cat == "Viral") %>% filter(cluster_id %in% c(1,2,3,4,5,6,7)) %>% select(cluster_id, Epitope) %>% unique() %>% arrange(cluster_id)
```

```{r}
top_viral_epitope <- res_tumor_selected_virus$node_data %>% filter(peptide_cat == "Viral") %>% group_by(Epitope) %>% mutate(n_epitope = n()) %>% arrange(desc(n_epitope))
table(top_viral_epitope$Epitope)

top_pep_viral_plot_list <- c("AVFDRKSDAK","FLYALALLL","GLCTLVAML","RTQSPRRR","YVLDHLIVV")
```

```{r}
top_tumor_epitope <- res_tumor_selected_virus$node_data %>% filter(peptide_cat == "Tumor") %>% group_by(Epitope) %>% mutate(n_epitope = n()) %>% arrange(desc(n_epitope))
table(top_tumor_epitope$Epitope)

top_pep_tumor_plot_list <- c("KVPRNQDWL","ALIHHNTHL","ESITGSLGPLL","RLPSSADVEF")

res_tumor_selected_virus$node_data <- res_tumor_selected_virus$node_data %>% mutate(top_pep_tumor_viral_plot_list = ifelse(Epitope %in% top_pep_tumor_plot_list,paste(Epitope,"Tumor",sep = "_"),ifelse(Epitope %in% top_pep_viral_plot_list,paste(Epitope,"Viral",sep = "_"),NA)))  %>% mutate(top_pep_tumor_plot_list = ifelse(Epitope %in% top_pep_tumor_plot_list,paste(Epitope,"Tumor",sep = "_"),NA))

table(res_tumor_selected_virus$node_data$top_pep_tumor_viral_plot_list)
```

```{r}
check_res <- addPlots(res_tumor_selected_virus,color_nodes_by = c("top_pep_tumor_viral_plot_list","top_pep_tumor_plot_list","outcome"))
```
```{r}
pdf("all_peptide_labels_and_viral.pdf")
  check_res
dev.off()
```

```{r}
network_graph_node_color_tumor_viral <- layer_data(check_res$plots$top_pep_tumor_viral_plot_list, 2)
network_graph_node_color_tumor_viral
```
```{r}
peptide_color_list = data.frame(peptide = check_res$node_data$top_pep_tumor_viral_plot_list, color = network_graph_node_color_tumor_viral$colour) %>% unique()
```
```{r}
peptide_color_list$peptide
peptide_color_list$color
```



```{r}
table(res_tumor_selected_virus$node_data$peptide_cat_col)
table(res_tumor_selected_virus$node_data$top_pep_tumor_plot_list)
```


```{r}
res_tumor_selected_virus$node_data %>% filter(peptide_cat == "Tumor") %>% arrange(cluster_id)
```

```{r}
res_tumor_selected_virus$node_data <- res_tumor_selected_virus$node_data %>%
  mutate(
    tumor_peptide_color = case_when(
      is.na(top_pep_tumor_plot_list) ~ "grey",
       # str_detect(top_pep_tumor_plot_list, 'RTQSPRRR_Viral')~ '#DB72FB',
       str_detect(top_pep_tumor_plot_list,  'ESITGSLGPLL_Tumor')~ '#93AA00',
       # str_detect(top_pep_tumor_plot_list,  'AVFDRKSDAK_Viral')~ '#D39200',
       # str_detect(top_pep_tumor_plot_list,  'YVLDHLIVV_Viral')~ '#FF61C3',
       str_detect(top_pep_tumor_plot_list,  'KVPRNQDWL_Tumor')~ '#00B9E3',
       # str_detect(top_pep_tumor_plot_list,  'FLYALALLL_Viral')~ '#00BA38',
       str_detect(top_pep_tumor_plot_list,  'RLPSSADVEF_Tumor')~ '#619CFF',
       # str_detect(top_pep_tumor_plot_list,  'GLCTLVAML_Viral')~ '#00C19F',
       str_detect(top_pep_tumor_plot_list,  'ALIHHNTHL_Tumor')~ '#F8766D',
      TRUE ~ NA_character_
    )
  )

tumor_peptide_color_list_no_NA <- peptide_color_list %>% drop_na() %>% filter(str_detect(peptide,"Tumor")) %>% arrange(peptide)
# cl_order <- network_node_dat %>% select(final_cell_type_color,final_cell_type) %>% unique() %>% arrange(final_cell_type)


jpeg("top_tumor_peptide_plot.jpeg",width = 7, height = 7, units = "in", res = 300)
ggraph(network_celltype_graph, layout= res_tumor_selected_virus$plots$graph_layout ) + geom_edge_link(edge_width = 0.1, color = "grey") + geom_node_point(size = 0.5, aes(color = res_tumor_selected_virus$node_data$tumor_peptide_color))  +
    scale_color_identity(guide = "legend", name = paste("Peptie"),
      # 1. Define the physical order of colors you want in the legend
      breaks = tumor_peptide_color_list_no_NA$color, 
      
      # 2. Match the labels to the exact order of the breaks above
      labels = tumor_peptide_color_list_no_NA$peptide) + coord_cartesian(xlim = x_limits, ylim = y_limits)+ guides(color = guide_legend(override.aes = list(size = 4))) + theme_void()
# pdf("./top_tumor_peptide_plot.pdf", width = 7, height = 7)
# top_tumor_peptide_plot
dev.off()
```
```{r}
pdf("top_tumor_viral_peptide_plot.pdf", check_res$plot$top_pep_tumor_viral_plot_list, width = 7, height = 7)
check_res$plot$top_pep_tumor_viral_plot_list
dev.off()
```

```{r}
res_tumor_selected_virus$node_data %>% write.csv("network_expanded_cluster_id.csv")
```

```{r}
res_tumor_selected_virus$node_data <- res_tumor_selected_virus$node_data %>%
  mutate(
    viral_peptide_color = case_when(
      is.na(top_pep_tumor_viral_plot_list) ~ "grey",
       str_detect(top_pep_tumor_viral_plot_list, 'RTQSPRRR_Viral')~ '#DB72FB',
       # str_detect(top_pep_tumor_plot_list,  'ESITGSLGPLL_Tumor')~ '#93AA00',
       str_detect(top_pep_tumor_viral_plot_list,  'AVFDRKSDAK_Viral')~ '#D39200',
       str_detect(top_pep_tumor_viral_plot_list,  'YVLDHLIVV_Viral')~ '#FF61C3',
       # str_detect(top_pep_tumor_plot_list,  'KVPRNQDWL_Tumor')~ '#00B9E3',
       str_detect(top_pep_tumor_viral_plot_list,  'FLYALALLL_Viral')~ '#00BA38',
       # str_detect(top_pep_tumor_plot_list,  'RLPSSADVEF_Tumor')~ '#619CFF',
       str_detect(top_pep_tumor_viral_plot_list,  'GLCTLVAML_Viral')~ '#00C19F',
       # str_detect(top_pep_tumor_plot_list,  'ALIHHNTHL_Tumor')~ '#F8766D',
      TRUE ~ NA_character_
    )
  )

viral_peptide_color_list_no_NA <- peptide_color_list %>% drop_na() %>% filter(str_detect(peptide,"Viral")) %>% arrange(peptide)
# cl_order <- network_node_dat %>% select(final_cell_type_color,final_cell_type) %>% unique() %>% arrange(final_cell_type)


jpeg("top_viral_peptide_plot.jpeg",width = 7, height = 7, units = "in", res = 300)
ggraph(network_celltype_graph, layout= res_tumor_selected_virus$plots$graph_layout ) + geom_edge_link(edge_width = 0.1, color = "grey") + geom_node_point(size = 0.5, aes(color = res_tumor_selected_virus$node_data$viral_peptide_color))  +
    scale_color_identity(guide = "legend", name = paste("Peptie"),
      # 1. Define the physical order of colors you want in the legend
      breaks = viral_peptide_color_list_no_NA$color, 
      
      # 2. Match the labels to the exact order of the breaks above
      labels = viral_peptide_color_list_no_NA$peptide) + coord_cartesian(xlim = x_limits, ylim = y_limits)+ guides(color = guide_legend(override.aes = list(size = 4))) + theme_void()
# pdf("./top_tumor_peptide_plot.pdf", width = 7, height = 7)
# top_tumor_peptide_plot
dev.off()
```

